---
title: "**Results Template**"
subtitle: "A Subtitle"
output:
  html_document:
    theme: cerulean
    highlight: "pygments"
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
    df_print: "kable"
    code_folding: hide
    code_download: true
  word_document:
    reference_docx: utils/Template_Word.docx
    highlight: "pygments"
    toc: false
    toc_depth: 3
    df_print: "kable"
    number_sections: true
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
bibliography: utils/bibliography.bib
csl: utils/apa.csl
---


<!-- 
!!!! IMPORTANT !!!!

Do not Knit this document by pressing the 'Knit' button. 

Instead, run `source("utils/render.R")` in the console (or the relevant lines in that file). 

If not, it will create the output in the same folder, whereas we want to keep it tidy in separate folders. 
-->

```{r setup, include=FALSE}
source("utils/config.R")  # Set up the environment

fast <- FALSE  # Make this false to skip the chunks
```

# Introduction

This is a template for a data analysis folder that can be easily exported as a [**webpage**](https://realitybending.github.io/ResultsTemplate/) or as **Supplementary Materials** (e.g., as a [word document](https://realitybending.github.io/ResultsTemplate/word/)). The README page of the repository, alongside the webpage and word document, were all created from this single [index.Rmd](https://github.com/RealityBending/ResultsTemplate/blob/main/index.Rmd) that you can edit.


- How to use this template?

Download it ([**click here to download**](https://github.com/RealityBending/ResultsTemplate/archive/main.zip)), unzip it and edit.

- How to upload it to a website?

Upload the whole folder to GitHub, go to settings and enable GitHub pages, and select the `docs/` folder as the location of the webpage. Indeed, rendering (knitting) the files will generate an "index.html" file in the `/docs/` folder, which is used as the website. You can see an example at [https://realitybending.github.io/ResultsTemplate/](https://realitybending.github.io/ResultsTemplate/).

- How to add references?

References have to be added in `bib` format in the [*utils/bibliography.bib*](https://github.com/RealityBending/ResultsTemplate/blob/main/utils/bibliography.bib) file, and further referenced in the text like this [@ludecke2019insight].


# Packages & Data

## Packages

```{r warning=FALSE, message=TRUE, results='asis'}
library(easystats)

summary(report::report(sessionInfo()))
```

## Data

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data.csv")

cat(paste("The data consists of", 
          report::report_participants(df, 
                                      participants = "Participant", 
                                      age = "Age")))
```

# Descriptive Stats {.tabset}

```{r, child=if (fast == FALSE) '1_descriptive.Rmd'}
```


# Package References

```{r warning=FALSE, message=FALSE, results='asis'}
report::cite_packages(sessionInfo())
```

# References
